Vulnerability Analysis of Container Images in Neuroimaging

### 2020-05-22 paper.tex
Feedback 2/2

\tristan{The scanner descriptions need to be streamlined.}

@@

BIDS app and Boutiques images that we took for our experiments have diverse Linux
distributions such as Ubuntu, Centos, Debian, and Alpine. Further, a particular
distribution can have different releases. As images in our experiments mostly have
Ubuntu distribution we can take this distribution as an example. In the case of Ubuntu, release
can be of two types: regular or LTS (Long Term Support).
Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of Extended Security Maintenance (ESM) release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. The ESM support period is decided by
Ubuntu. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
data in vulnerability databases because after EOL of a release, a vulnerability is fixed only in packages of ESM, however, it still
exists in LTS.

@@

If there exist vulnerabilities in the container image, then we can
run after updating the
image. Updating the image involves updating all software packages that are
inside that image. We used a bash script (\href{https://github.com/kaurbhupinder/Vulnerability-Analysis}{Github}) 
to update all images, which checks the
package manager present inside the image and then according to that it
updates the image. However, this option affects the reproducibility
of the image, which means that the image cannot be used to verify the research
findings of other scientists.

\subsection{Image size Reduction process}
If we want to reduce the number of vulnerabilities without effecting the reproducibility of the image,
image size reduction process is a good choice. In this process, we reduce the number of packages
installed in the image by deleting unnecessary packages. For that to happen, we need to first figure
out which packages we need for the pipeline to function properly. Here, we used 
Reprozip~\cite{rampin2016reprozip}. It is a tool that
is used to make applications reproducible. It traces operating system calls used by the
application while execution and then based on that it recognizes binaries, files, environment variables,
and library dependencies that will be used by the application for future re-execution. If the OS is
Debian or RPM-based, Reprozip also
uses an available package manager to acquire a list of distribution packages from where these files come from.
So, we got a list of packages from Reprozip that are needed for the application execution. 
After that, we expanded this list by adding important and required packages that are essential
for the system to function and finally figured out all the dependencies of these packages using Debtree
~\cite{debtree}.
Ultimately, we kept these packages and removed remaining unnecessary packages. We used a bash script
(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/script.sh}{Github}) for
the image size reduction process which installs Reprozip in the image, collects Reprozip trace, and
finally deletes unnecessary packages.

@@

@@

In this section,
we first discuss the existing vulnerabilities in the images and compare the
results of the three scanners. Then we discuss the effect of the update on the
existing vulnerabilities followed by the results of the image size reduction
process. Lastly, this section presents the combined effect of update and image size reduction on the
vulnerabilities. Here, we want to mention that after the update and minification process we scanned
images only with one scanner i.e Anchore. We selected Anchore out of three scanners at random.

@@

Table~\ref{sing} shows the number of vulnerabilities present in Singularity images whereas 
Figure~\ref{fig:venn} illustrates the number of vulnerabilities in Docker images, which are detected by the three scanners. The
overlapping regions of the Venn diagram show the number of common vulnerabilities detected by either two or
three scanners. In total 10691 vulnerabilities are detected by three scanners.
There are also vulnerabilities that are detected only by one scanner.

Figure~\ref{fig:graph1} gives more image-specific information.
It represents the number of vulnerabilities that are present inside images.
The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased.
The figure also infers that Alpine distribution, being the
lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains the highest number of
vulnerabilities. Debian and Centos contain a higher number of critical vulnerabilities than Ubuntu and Alpine.
Similarly, Figure~\ref{sing} illustrates the number of vulnerabilities in Singularity images used in Boutiques images.
\begin{table*}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\textwidth},
  after reading=\end{adjustbox},
 tabular={c |c | c | c | c |c},
	table head =Image Labels &{Image names} &{OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{results.csv}{}{\csvlinetotablerow}%
       \centering
	\caption{\label{table1}Existing number of Vulnerabilities}
\end{table*}
%\begin{comment}
%\begin{table}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c|c},
%	table head ={Image Tag} & {Image Name}\\\hline,
% late after line= \\,
%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{names.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{\label{table2}Image names}
%\end{table}
%\end{comment}
\begin{figure}
        {\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/vennDiagram.pdf}}
        \caption{\label{fig:venn} Venn Diagram representing different scanner results}
\end{figure}

@@

Table~\ref{table1} compares the results of scanning images with the three scanners.
Venn Diagram in Figure~\ref{fig:venn} summarizes this table.

@@

\textbf{CVEs with Status as “Not-affected”:} Vuls is reporting vulnerabilities that have status
as "not-affected" in the vulnerability database. So it means Linux distribution which is inside the image is not affected
by the particular CVE. However, it is reported by Vuls. In other words, we can say that
these are false positives by Vuls.
For example, we scanned an image having the Trusty release in it and Vuls is reporting CVE-2015-2305
in the package Cups. However, if we check the vulnerability database, package Cups in Trusty is not
affected by this CVE.

@@

\textbf{False negatives by Clair:} Clair is missing vulnerabilities that it should detect. For example, CVE-2016-9082 
is present in package Cairo in Xenial release and it is not detected by Clair.

@@

Our third experiment involves deleting unnecessary packages from the images.
We did this experiment only on five images because the reduction process takes a
while. We selected these five images at random. We noticed that
after the size reduction process, the scanning results deviate a little from our initial belief.
At first, we thought that we will have a notable effect of size reduction on
vulnerabilities. However, this is not the case always. The bar graph shown in
Figure~\ref{fig:bargraph} illustrates that images \textit{bids/ndmg} and
\textit{poldracklab/fmriprep:1.2.3} have an insignificant effect of size reduction.
According to our analyzes here, this can be due to two reasons: \rom{1}) the number
and \rom{2}) the kind of packages that we deleted. In other
words, if we delete a low number of packages then vulnerabilities do not get decreased as expected.
In contrast, if the number of deleted packages are high, reduction
in vulnerabilities also becomes high. For instance, we were able to delete only 21 and 25 packages for 
\textit{bids/ndmg} and \textit{poldracklab/fmriprep:1.2.3} images. Consequently, vulnerabilities
reduced only by 4 and 17 respectively. Furthermore, this is illustrated in Figure~\ref{deleted}.
Also, if we delete packages that contain a lot of vulnerabilities, it helps in reducing
vulnerabilities by a significant number. For instance, in case of our experiments
deleting compilers and Linux-kernel-header packages helped to minimize vulnerabilities
by a significant number in \textit{bids/example, bids/freesurfer, and bids/mindboggle:0.0.4-1}. 
%Our third experiment shows that deleting unnecessary packages from the image also helps to reduce
%the number of vulnerabilities by a significant number. We started this experiment with
%\textit{bids/example} image and deleted 61 unnecessary packages out of total 528 packages, which helped
%to reduce 838 vulnerabilities to 523. Later, we also checked with \textit{bids/freesurfer} image, which allowed
%to delete 71 unnecessary packages out of total 298 packages. Consequently, reducing number of vulnerabilities
%from 353 to 101.

\subsection{Effect Of Update and Size Reduction}

Our last experiment includes updating the image and then removing unnecessary packages from it.
Figure~\ref{fig:bargraph} displays the results. 
Our initial thought was that with the update and size reduction process together, we will be able to
reduce vulnerabilities even more. However
we analyzed that this is not always true. Again, it depends on which packages you are deleting and how
many vulnerabilities they contained. To illustrate, \textit{bids/example} image in Figure~\ref{fig:bargraph}
shows no effect of size reduction along with update process. It has 181 vulnerabilities for both experiments 2 and 4.
Meaning that packages, which we deleted after updating the image, were already vulnerability free. Therefore,
scanning results did not change.

@@

@@

In this paper, we performed various experiments to study the security state of the Docker
and Singularity images, which are used in the neuroimaging field. We found out strong correlation
between the number of packages and the number of vulnerabilities in the images, which implies
that the number of vulnerabilities increases with the number of packages. We also found out that
updating images reduces the number of vulnerabilities by a significant number. However, for some
vulnerabilities there are no fixes available yet so the images cannot 
be made totally invulnerable. Continuing with our next two experiments, we analyzed that the
image size reduction process also reduces vulnerabilities a lot. However, we found out that this is not
always true. It depends on two factors: kind and the number of packages that we are
deleting. Therefore, we conclude this paper by suggesting ten simple rules that can be
followed to keep container images safe.
\newline 1. Update packages regularly.
\newline 2. Remove unnecessary packages.
\newline 3. Mind your base OS image.
\newline 4. Run image scanning tools in CI scripts. For instance Anchore.
\newline 5. Mind your GitHub/DockerHub credentials.
\newline 6. Minimize dependencies.
\newline 7. Avoid static linking because it obfuscates vulnerability scanning.
\newline 8. Use the package manager to facilitate vulnerability detection.
\newline 9. Use OS releases that have LTS support.
\newline 10. Sign your images.

>>>>

\tristan{The scanner descriptions need to be streamlined. They are quite verbose and not very consistent for now.}

@@

\tristan{This section lacks a sentence to introduce context: why are you even talking about distributions? 
You should explain that scanners report vulnerabilities differently depending on the release type. 
Also, is there a similar scheme in CentOS? }

BIDS app and Boutiques images that we took for our experiments have diverse Linux
distributions such as Ubuntu, Centos, Debian, and Alpine. Further, a particular
distribution can have different releases. As images in our experiments mostly have
Ubuntu distribution we can take this distribution as an example \tristan{of what?}. In the case of Ubuntu, release
can be of two types: regular or LTS (Long Term Support).
Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of Extended Security Maintenance (ESM) release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. The ESM support period is decided by
Ubuntu. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
data in vulnerability databases because after EOL of a release, a vulnerability is fixed only in packages of ESM, however, it still
exists in LTS.

@@

\tristan{since the next 3 sections are rather short, I would group them all 
as paragraphs under the same sub-section.}

If there exist vulnerabilities in the container image, then we can
run after updating the
image. Updating the image involves updating all software packages that are
inside that image. We used a bash script (\href{https://github.com/kaurbhupinder/Vulnerability-Analysis}{Github} \tristan{link should point to the actual script, not the repo}) 
to update all images, which checks the
package manager present inside the image and then according to that it
updates the image. However, this option affects the reproducibility
of the image, which means that the image cannot be used to verify the research
findings of other scientists.

\subsection{Image size Reduction process}
If we want to reduce the number of vulnerabilities without effecting the reproducibility of the image,
image size reduction process is a good choice. In this process, we reduce the number of packages
installed in the image by deleting unnecessary packages. For that to happen, we need to first figure
out which packages we need for the pipeline to function properly. Here, we used 
Reprozip~\cite{rampin2016reprozip}. It is a tool that
is used to make applications reproducible. It traces operating system calls used by the
application while execution and then based on that it recognizes binaries, files, environment variables,
and library dependencies that will be used by the application for future re-execution. If the OS is
Debian or RPM-based, Reprozip also
uses an available package manager to acquire a list of distribution packages from where these files come from.
So, we got a list of packages from Reprozip that are needed for the application execution. 
After that, we expanded this list by adding important and required packages that are essential
for the system to function and finally figured out all the dependencies of these packages using Debtree
~\cite{debtree}.
Ultimately, we kept these packages and removed remaining unnecessary packages. We used a bash script
(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/script.sh}{Github} \tristan{Link is broken}) for
the image size reduction process which installs Reprozip in the image, collects Reprozip trace, and
finally deletes unnecessary packages.

\tristan{You should explain why you didn't use Neurodocker as it's the obvious way to do this.}

@@

\tristan{This could go to the first sentences of the new sub-section, no need for a subsection for that.}

@@

In this section,
we first discuss the existing vulnerabilities in the images and compare the
results of the three scanners. Then we discuss the effect of the update on the
existing vulnerabilities followed by the results of the image size reduction
process. Lastly, this section presents the combined effect of update and image size reduction on the
vulnerabilities. Here, we want to mention that after the update and minification process we scanned
images only with one scanner i.e Anchore. We selected Anchore out of three scanners at random \tristan{Probably not really at random... 
No need to mention anything if it was completely arbitrary. You should mention that just in the experiments themselves, it's giving this comment too much importance to put it here.}.

@@

Table~\ref{sing} shows the number of vulnerabilities present in Singularity
images whereas Figure~\ref{fig:venn} illustrates the number of
vulnerabilities in Docker images, which are detected by the three scanners.
\tristan{You should refer to tables in the order they are presented (1
first, then 2). Tables should also be located next to their reference. In
this case I would actually create a single table, greying out cells that
aren't pertinent (Anchore, Vuls and Clair for Singularity images.)}
 The
overlapping regions of the Venn diagram show the number of common vulnerabilities detected by either two or
three scanners. In total 10691 vulnerabilities are detected by three scanners.
There are also vulnerabilities that are detected only by one scanner. \tristan{The last 3 sentences bring absolutely no 
extra information that can't be read on the figure directly. You should replace them with only 1 sentence noting that there 
are important discrepancies between scanner results (maybe quantify that with a Dice or Jaccard coefficient). This is an example 
of how writing should be improved throughout the paper.}

Figure~\ref{fig:graph1} gives more image-specific information.
It represents the number of vulnerabilities that are present inside images.
The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased \tristan{mention the parameters of the regression line (preferably as a label in the figure) and the regression error}.
The figure also infers that Alpine distribution, being the
lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains the highest number of
vulnerabilities. Debian and Centos contain a higher number of critical vulnerabilities than Ubuntu and Alpine \tristan{I dont think there is enough data to 
claim that, claim should be softened.}.
Similarly, Figure~\ref{sing} \tristan{there is a reference error, and if it's still a different figure I think you should make only 1.} illustrates the number of vulnerabilities in Singularity images used in Boutiques images.
\tristan{In the Figure, could you increase the marker size in the caption, and order it so that the different versions of a distribution 
are grouped together and sorted by increasing version?}
\begin{table*}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\textwidth},
  after reading=\end{adjustbox},
 tabular={c |c | c | c | c |c},
	table head =Image Labels &{Image names} &{OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{results.csv}{}{\csvlinetotablerow}%
       \centering
	\caption{\label{table1}Existing number of Vulnerabilities}
\end{table*}
%\begin{comment}
%\begin{table}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c|c},
%	table head ={Image Tag} & {Image Name}\\\hline,
% late after line= \\,
%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{names.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{\label{table2}Image names}
%\end{table}
%\end{comment}
\begin{figure}
        {\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/vennDiagram.pdf}}
        \caption{\label{fig:venn} Venn Diagram representing different scanner results}
\end{figure}

@@

Table~\ref{table1} compares the results of scanning images with the three scanners.
Venn Diagram in Figure~\ref{fig:venn} summarizes this table. \tristan{You said it already.}

@@

\textbf{CVEs with Status as “Not-affected”:} Vuls is reporting vulnerabilities that have status
as "not-affected" in the vulnerability database. So it means Linux distribution which is inside the image is not affected
by the particular CVE. However, it is reported by Vuls \tristan{do you mean Anchore? This sounds circular.}. In other words, we can say that
these are false positives \tristan{the use of ``false positives'' is ambiguous} by Vuls.
For example, we scanned an image having the Trusty release in it and Vuls is reporting CVE-2015-2305
in the package Cups. However, if we check the vulnerability database, package Cups in Trusty is not
affected by this CVE.

@@

\textbf{False negatives by Clair:} Clair is missing vulnerabilities that it should detect. For example, CVE-2016-9082 
is present in package Cairo in Xenial release and it is not detected by Clair. \tristan{You should report the version of Clair in 
the methods. If you reported this bug to the developers, you should say so and link it here (same comment for all the bugs).}

@@

Our third experiment involves deleting unnecessary packages from the images.
We did this experiment only on five images because the reduction process takes a
while \tristan{This is not a good argument, it is vague, and it is not complete. Size reduction also requires 
to run a pipeline in the image.}. We selected these five images at random \tristan{really? I don't think so.}. We noticed that
after the size reduction process, the scanning results deviate a little from our initial belief \tristan{what do you mean?}.
At first, we thought that we will have a notable effect of size reduction on
vulnerabilities. However, this is not the case always. The bar graph shown in
Figure~\ref{fig:bargraph} illustrates that images \textit{bids/ndmg} and
\textit{poldracklab/fmriprep:1.2.3} have an insignificant effect of size reduction.
According to our analyzes here, this can be due to two reasons: \rom{1}) the number
and \rom{2}) the kind of packages that we deleted. In other
words, if we delete a low number of packages then vulnerabilities do not get decreased as expected.
In contrast, if the number of deleted packages are high, reduction
in vulnerabilities also becomes high. For instance, we were able to delete only 21 and 25 packages for 
\textit{bids/ndmg} and \textit{poldracklab/fmriprep:1.2.3} images. Consequently, vulnerabilities
reduced only by 4 and 17 respectively. Furthermore, this is illustrated in Figure~\ref{deleted} \tristan{I'm not thrilled by this figure, I would 
just mention in the text that we verified that.}.
\tristan{The next sentence is interesting because it starts characterizing the images that benefit the most 
from size reduction. The previous sentences read like a tautology, you should make your comment more specific.} 
Also, if we delete packages that contain a lot of vulnerabilities, it helps in reducing
vulnerabilities by a significant number. For instance, in case of our experiments
deleting compilers and Linux-kernel-header packages helped to minimize vulnerabilities
by a significant number in \textit{bids/example, bids/freesurfer, and bids/mindboggle:0.0.4-1}. 
%Our third experiment shows that deleting unnecessary packages from the image also helps to reduce
%the number of vulnerabilities by a significant number. We started this experiment with
%\textit{bids/example} image and deleted 61 unnecessary packages out of total 528 packages, which helped
%to reduce 838 vulnerabilities to 523. Later, we also checked with \textit{bids/freesurfer} image, which allowed
%to delete 71 unnecessary packages out of total 298 packages. Consequently, reducing number of vulnerabilities
%from 353 to 101.

\subsection{Combined Effect Of Update and Size Reduction}

Our last experiment includes updating the image and then removing unnecessary packages from it.
Figure~\ref{fig:bargraph} displays the results. 
Our initial thought was that with the update and size reduction process together, we will be able to
reduce vulnerabilities even more. However
we analyzed that this is not always true. Again, it depends on which packages you \tristan{in general don't use ``you'' in a 
formal paper.} are deleting and how
many vulnerabilities they contained. To illustrate, \textit{bids/example} image in Figure~\ref{fig:bargraph}
shows no effect of size reduction along with update process. It has 181 vulnerabilities for both experiments 2 and 4.
Meaning that packages, which we deleted after updating the image, were already vulnerability free. Therefore,
scanning results did not change.

@@

\tristan{You should comment on the important number of vulnerabilities found in the images overall.}

@@

In this paper, we performed various experiments to study the security state of the Docker
and Singularity images, which are used in the neuroimaging field. We found out strong correlation
between the number of packages and the number of vulnerabilities in the images, which implies
that the number of vulnerabilities increases with the number of packages. We also found out that
updating images reduces the number of vulnerabilities by a significant number. However, for some
vulnerabilities there are no fixes available yet so the images cannot 
be made totally invulnerable. Continuing with our next two experiments, we analyzed that the
image size reduction process also reduces vulnerabilities a lot. However, we found out that this is not
always true. It depends on two factors: kind and the number of packages that we are
deleting. Therefore, we conclude this paper by suggesting ten simple rules that can be
followed to keep container images safe.
\newline 1. Update packages regularly.
\newline 2. Remove unnecessary packages, in particular the ones used for installation (compilers, source packages, etc).
\newline 3. Mind your base OS image.
\newline 4. Run image scanning tools in CI scripts. For instance Anchore.
\newline 5. Mind your GitHub/DockerHub credentials.
\newline 6. Minimize dependencies.
\newline 7. Avoid static linking because it obfuscates vulnerability scanning.
\newline 8. Use the package manager to facilitate vulnerability detection.
\newline 9. Use OS releases that have LTS support.
\newline 10. Sign your images.

\tristan{You should discuss future work here too.}
